Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 ms.tex

We have presented stellar parameters for all planet candidates systems identified by
\paperit.
We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
identify four as false positives.
Of these planets, 4 have been previously validated in other works, while 17 are
validated here for the first time.
The 11 systems not validated as planets or false positives remain as planet candidates.

>>>>

We have presented stellar parameters for all planet candidates systems identified by
\paperit.
We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
identify \Nfp\ as false positives.
Of these planets, 4 have been previously validated in other works, while 14 are
validated here for the first time.
The systems not validated as planets or false positives remain as planet candidates.

Enabling much of this analysis are two new open-source Python packages: 
\texttt{isochrones}\footnote{\url{http://github.com/timothydmorton/isochrones}}, 
which we use to infer posteriors on physical stellar properties based
on fitting theoretical stellar models to observed data; and \texttt{vespa}\footnote{
\url{http://github.com/timothydmorton/vespa}}, a
new implementation of the \citet{Morton12} transit false positive analysis scheme.  
Both of these packages will continue to be useful in future analysis of transit candidates
where comprehensive follow-up observations may be unavailable.
